Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-08-21 parts/summary.tex
continuing response
editing

The way of discovering lenses is changing with the introduction of
machine learning and citizen science, combined with the coverage of
huge areas by modern surveys.  The way mass models also needs to
change, in order to be prepared for the increasing influx of lenses to
be modelled.  This work is a hybrid of the classical style, where a
small team of experts invest many hours into the creation of a single
model, with the approach of citizen science, where a crowd of amateur
volunteers make independent contributions.  We are a collaboration of
professionals and experienced citizen-science volunteers, aiming to
create early-stage lens models as soon as a lens candidate is found.

@@

Figure~\ref{fig:stelmass} is another summary.  It shows most of the
candidates having stellar and total mass typical of massive
ellipticals.  SW05 is one of the most massive of all the candidates, with a
mass of galaxy-group scale.  It is a particularly attractive system
for follow-up observations at higher resolution, as it is a large system
with clear multiple-image features, and modelling leaves little doubt
that it is a lens.
SW04 seems to be even more massive, but the diagnostics leave some doubts
about this model.
The two lowest-mass systems, SW19 and SW42, are
important if they are indeed lenses, because of their low mass.
The models in both cases are plausible but not entirely satisfactory.
Their follow up, especially the one on SW42, would either confirm that
abundance matching and the halo-matching index $\haloindex$ are good
criteria for filtering possible candidates or it would lead to a really
interesting new, very low mass galaxy that is highly dominated by dark matter.

>>>>

The way of discovering lenses is changing with the introduction of
machine learning and citizen science, combined with the coverage of
huge areas by modern surveys.  The way mass models are constructed also needs to
change, in order to be prepared for the increasing influx of lenses to
be modelled.  This work is a hybrid of the classical style, where a
small team of experts invest many hours into the creation of a single
model, with the approach of citizen science, where a crowd of amateur
volunteers make independent contributions.  We are a collaboration of
professionals and experienced citizen-science volunteers, aiming to
create early-stage lens models as soon as a lens candidate is found.

@@
